Wind Veer and Speed in Turbulent Ekman Flow Part I: Scaling analysis and universal profile model

### 2024-11-07 write1/manuscript.tex
Fixed labels and numbering of appendices

\appendix

\section*{Appendix A: Laminar Ekman solution with consideration of inner layer}
\label{app:ekman_solution}
The following Ekman system is obtained by averaging the Navier--Stokes equations horizontally and over time and neglecting the turbulent transport terms (turbulence can then be considered via the eddy-viscosity concept through variations in the viscosity $\nu$):
\begin{subequations}
\begin{eqnarray}
  \left(\begin{matrix}
    \p_t U\\
    \p_t V  
  \end{matrix}\right)&=&\left(\begin{matrix}
     fV &+& \nu \p_z^2 U\\ 
    -f(U-G) &+& \nu \p_z^2 V
  \end{matrix}\right)\\ 
  \Rightarrow \partial_t (U+iV) &=& f(V-i(U-G))) + \nu \p_z^2(U+iV)
\end{eqnarray}
In stationary conditions, this system is solved by
\begin{eqnarray}
  \hat{u}(z) &=& U_{\infty} + e^{-\gamma z} \left[A \cos\gamma z + B \sin\gamma z\right]   \\
  \hat{v}(z) &=& V_{\infty} + e^{-\gamma z} \left[-A \sin\gamma z + B \cos\gamma z\right]
\end{eqnarray} 
\end{subequations}
where the constants $U_\infty$, $V_\infty$ set the top boundary condition and $A$ and $B$ set the bottom boundary condition. 
%
The most common boundary condition for a surface Ekman layer is $A=U_{\infty}=G$, $B=0$, and $V_{\infty}=0$.
%
The lower boundary condition, however, neglects the existence of the surface layer, and it appears reasonable to define
$A=c G$ where $c<1$ is a constant that incorporates the increased shear in the surface layer.
%
Given a 'matching height' $z_{match}$ and normalized matching height $\xi=\gamma z_\text{match}$ in the upper part of the inner layer, we can match the Ekman profile
to the inner layer by letting
%
\begin{subequations}
\begin{eqnarray}
  \begin{matrix} 
    u(z_\text{match}) \equiv u_\text{match} &=& U_{\infty} + e^{-\gzm} \left [ A \cos\gzm + B\sin\gzm \right] \\
    v(z_\text{match}) \equiv v_\text{match} &=& V_{\infty} + e^{-\gzm} \left [-A \sin\gzm + B\cos\gzm \right]
  \end{matrix} 
\end{eqnarray}
\begin{eqnarray}
  \Rightarrow \left(\begin{matrix}
    u_\text{match}-U_{\infty} \\ 
    v_\text{match}-V_{\infty}
  \end{matrix}\right) = e^{-\gzm}\left(\begin{matrix}A \\ B \end{matrix}\right)\left(\begin{matrix}
    \cos\gzm &+ \sin\gzm \\ -\sin\gzm &+ \cos\gzm
  \end{matrix} \right) \\
\end{eqnarray}
\end{subequations}
Matching the profile at $\xi=0$, one obtains
$A = \Delta u_\text{match} $ and $B=-\Delta w_\text{match} $; and when the direction $Ox$ is aligned
with the geostrophic wind, we obtain the textbook-case $A=|\mathbf{G}|$ and $B=0$.

@@

\section*{Appendix B: Matching the spanwise velocity profiles in the inner layer}

>>>>

\appendix
\section{Appendices}
\subsection{Laminar Ekman solution with consideration of inner layer}
\label{app:ekman_solution}
The following Ekman system is obtained by averaging the Navier--Stokes equations horizontally and over time and neglecting the turbulent transport terms (turbulence can then be considered via the eddy-viscosity concept through variations in the viscosity $\nu$):
\begin{subequations}
\begin{eqnarray}
  \left(\begin{matrix}
    \p_t U\\
    \p_t V  
  \end{matrix}\right)&=&\left(\begin{matrix}
     fV &+& \nu \p_z^2 U\\ 
    -f(U-G) &+& \nu \p_z^2 V
  \end{matrix}\right)\\ 
  \Rightarrow \partial_t (U+iV) &=& f(V-i(U-G))) + \nu \p_z^2(U+iV)
\end{eqnarray}
In stationary conditions, this system is solved by
\begin{eqnarray}
  \hat{u}(z) &=& U_{\infty} + e^{-\gamma z} \left[A \cos\gamma z + B \sin\gamma z\right]   \\
  \hat{v}(z) &=& V_{\infty} + e^{-\gamma z} \left[-A \sin\gamma z + B \cos\gamma z\right]
\end{eqnarray} 
\end{subequations}
where the constants $U_\infty$, $V_\infty$ set the top boundary condition and $A$ and $B$ set the bottom boundary condition. 
%
The most common boundary condition for a surface Ekman layer is $A=U_{\infty}=G$, $B=0$, and $V_{\infty}=0$.
%
The lower boundary condition, however, neglects the existence of the surface layer, and it appears reasonable to define
$A=c G$ where $c<1$ is a constant that incorporates the increased shear in the surface layer.
%
Given a 'matching height' $z_{match}$ and normalized matching height $\xi=\gamma z_\text{match}$ in the upper part of the inner layer, we can match the Ekman profile
to the inner layer by letting
%
\begin{subequations}
\begin{eqnarray}
  \begin{matrix} 
    u(z_\text{match}) \equiv u_\text{match} &=& U_{\infty} + e^{-\gzm} \left [ A \cos\gzm + B\sin\gzm \right] \\
    v(z_\text{match}) \equiv v_\text{match} &=& V_{\infty} + e^{-\gzm} \left [-A \sin\gzm + B\cos\gzm \right]
  \end{matrix} 
\end{eqnarray}
\begin{eqnarray}
  \Rightarrow \left(\begin{matrix}
    u_\text{match}-U_{\infty} \\ 
    v_\text{match}-V_{\infty}
  \end{matrix}\right) = e^{-\gzm}\left(\begin{matrix}A \\ B \end{matrix}\right)\left(\begin{matrix}
    \cos\gzm &+ \sin\gzm \\ -\sin\gzm &+ \cos\gzm
  \end{matrix} \right) \\
\end{eqnarray}
\end{subequations}
Matching the profile at $\xi=0$, one obtains
$A = \Delta u_\text{match} $ and $B=-\Delta w_\text{match} $; and when the direction $Ox$ is aligned
with the geostrophic wind, we obtain the textbook-case $A=|\mathbf{G}|$ and $B=0$.

@@

\subsection{Matching the spanwise velocity profiles in the inner layer}
